% Dr. Geoff Boeing - Curriculum Vitae
% Copyright 2019 Geoff Boeing
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?
\newcommand{\myname}{Yash Pote}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
            \setlength{\parskip}{0em}
            \setlength{\itemsep}{\listitemspace}
            \setlength{\parsep}{\listitemspace}}}
    {\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright

    % display name as the document title
    \namefont{\myname}

    % contact info
    \vspace{1em}
    \begin{minipage}[t]{0.68\textwidth}
        School of Computing \\
		National University of Singapore
        %\\Los Angeles, California, USA
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        Email: \href{mailto:yashppote@gmail.com}{yashppote@gmail.com} \\
        Web: \href{https://yashpote.com/}{https://yashpote.com/}
    \end{minipage}
    \vspace{0.5em}



    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab School of Computing, National University of Singapore, 2019-

        \item[B.Tech.]  \tab Computer Science and Engineering , IIT - Guwahati, 2014-2018

    \end{tablist}


    \section*{Research Areas}

    \begin{itemize}

        \item Urban informatics and spatial data science: computational statistics, visualization, and spatial analysis

        \item Transportation planning: access, equity, street network design, and urban form

        \item Housing: emerging technology platforms' impacts on markets, residential mobility, and segregation

    \end{itemize}



    \section*{Publications}

%    \subsection*{Articles in Peer-Reviewed Journals}
%
%    \begin{tablist}
%    	
%    \end{tablist}
%
%
%
%    \subsection*{Journal Article Manuscripts Under Review}
%
%    \begin{tablist}
%
%    \end{tablist}
%
%
%
%    \subsection*{Book Chapters}
%
%    \begin{tablist}
%
%    \end{tablist}



    \subsection*{Conference Proceedings/Compendia}

    \begin{tablist}

        \item[2019] \tab Boeing, G. \enquote{Street Network Patterns, Orientation, and Entropy around the World.} Compendium of the Transportation Research Board 98\textsuperscript{th} Annual Meeting. Washington, DC. Jan 13--17. \href{https://trid.trb.org/view/1573315}{https://trid.trb.org/view/1573315}

    \end{tablist}


%    \subsection*{Reports and Working Papers}
%
%    \begin{tablist}
%    \end{tablist}

    \subsection*{Manuscripts in Preparation}

    \begin{tablist}
        
        \item[\the\year] \tab Boeing, G. and W. Riggs. \enquote{Converting One-Way Streets to Two-Way Streets to Improve Transportation Network Efficiency and Reduce Vehicle Distance Traveled and Emissions.} Target: \textit{Journal of the American Planning Association}, Winter 2020.

    \end{tablist}



%    \section*{Invited Talks}
%
%    \begin{tablist}
%
%    \end{tablist}

    \subsection*{Campus Talks}

    \begin{tablist}

        \item[2017] \tab \enquote{Urban Street Network Analysis with OSMnx.} Geospatial Innovation Facility, College of Natural Resources, University of California, Berkeley. Berkeley, California. Oct 5.

    \end{tablist}

    \subsection*{Conference Presentations}

    Presenting author \textit{italicized} if other than first author.\bigskip
    % Asterisk* indicates paper published in \enquote{Peer-Reviewed Proceedings} above.

    \begin{tablist}
    	
    	%\item[2020] \tab Boeing, G. \enquote{OSMnx: Acquiring, Modeling, Analyzing, and Visualizing Street Networks and Related Urban Data with Python.} Python in Science (SciPy) Annual Conference. Austin, Texas. Jul 6--12.
    	
    	\item[2020] \tab Higgs, C.,  S. Liu, G. Boeing, J. Arundel, M. Lowe, J. Sallis, E. Cerin, A.~V. Moudon, E. Hinckson, D. Adlakha, and B. Giles-Corti. \enquote{Using Open Data to Measure Policy-Relevant Geospatial Indicators of Healthy, Active Urban Environments in 25 Global Cities.} International Society of Behavioral Nutrition and Physical Activity Annual Meeting. Auckland, New Zealand. June 17--20.
    	
    

    \end{tablist}





    \section*{Teaching Experience}

    \subsection*{University of Southern California}
    
    \begin{itemize}
    	
    	\item Urban Informatics
    	\item Data, Evidence, and Communication for the Public Good
    
	\end{itemize}
    	

    \section*{Professional Affiliations}

    \begin{itemize}

        \item American Association of Geographers

    \end{itemize}


    \section*{Professional Experience}

    \begin{tablist}

        \item[2009--13] \tab Accenture, Consultant and Project Manager\\
                             London, England; New York, New York; San Diego, California



    \end{tablist}



  



    \section*{Technical Skills}

    \subsection*{Statistical and Computational Methods}

    \begin{itemize}

        \item Computational statistics and machine learning, systems analysis, data mining, data wrangling, Python (including numpy, scipy, pandas, matplotlib, statsmodels, networkx, and scikit-learn), JavaScript, HTML, web scraping, MySQL, Postgres, and various other databases.

    \end{itemize}



    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        %\vspace{6em}
        \vfill
        Updated \monthyeardate\today
    \end{center}


\end{document}
